---
title: "R Notebook"
output: html_notebook
---


Euclidean rhythm calculator





Implementation

For our javascript implementation we utilize two functions. The first calculates the basic euclidean rhythm, given a number of steps and pulses, and stores it an array called storedRhythm as a sequence of 1’s and 0’s.

```
//calculate a euclidean rhythm
function euclid(steps,  pulses, rotation){
    storedRhythm = []; //empty array which stores the rhythm.
    //the length of the array is equal to the number of steps
    //a value of 1 for each array element indicates a pulse

    var bucket = 0; //out variable to add pulses together for each step

    //fill array with rhythm
    for( var i=0 ; i < steps ; i++){ 
        bucket += pulses; 
            if(bucket >= steps) {
            bucket -= steps;
            storedRhythm.push(1); //'1' indicates a pulse on this beat
        } else {
            storedRhythm.push(0); //'0' indicates no pulse on this beat
        }
    }
}
```

```{r}
euclid <- function(steps,pulses,rotation){
  storedRhythm <- vector(length=steps)
  bucket <- 0
  for(ii in 1:steps){
    bucket <- bucket + pulses
    if(bucket >= steps){
      bucket <- bucket - steps
      storedRhythm[ii]<-1
    }
    else{
      storedRhythm[ii]<-0
    }
    message(sprintf("%d",storedRhythm[ii]),appendLF = F)
  }
  message("")
  return(storedRhythm)
}
  
  
euclid(13,5,1)
  
euclid(13,10,1)
  
euclid(61,23,1)


```



```{Rcpp firstChunk}
#include <Rcpp.h>

//[[Rcpp::export]]
Rcpp::IntegerVector euclidpp(Rcpp::Integer steps, Rcpp::Integer pulses) {
  Rcpp::IntegerVector storedRhythm(steps);
  
  return storedRhythm;
}
```









The second function carries out the rotation:

```
function rotateSeq(seq, rotate){
    var output = new Array(seq.length); //new array to store shifted rhythm
    var val = seq.length - rotate;

    for( var i=0; i < seq.length ; i++){
        output[i] = seq[ Math.abs( (i+val) % seq.length) ];
    }

    return output;
}
```

Querying the current beat

Finally, we have a function for querying the storedRhythm array to find out if there is a pulse on the current beat:

```
//send triggers
    function query_beat(curBeat){
    var curStep = curBeat % curSteps; //wraps beat around if it is higher than the number of steps
    return storedRhythm[curStep];
}
```













*Replicating Bjorklund's 'figure 4' algorithm:*


The original looks like this :

```
void function compute_bitmap (int num_slots, int num_pulses)
{
    /*---------------------
    * First, compute the count and remainder arrays
    */
    divisor = num_slots – num_pulses;
    remainder[0] = num_pulses;
    level = 0;
    do {
        count[level] = divisor / remainder[level];
        remainder[level+1] = mod(divisor, remainder[level]);
        divisor = remainder[level];
        level = level + 1;
    }while (remainder[level] > 1);
    count[level] = divisor;
    /*---------------------
    * Now build the bitmap string
    */
    build_string (level);
} 
```


```{r}
require (stringr)
nslots <- 8
npulses <- 5
divisor <- nslots-npulses
remainder <- vector(length=nslots)

#REMEMBER! R is 1-indexed, C is 0-indexed
rem_lminus1 <- npulses
level <- 0

while(T){
  
  level<- level + 1
  if(level>10)
    break;
}



```
 ..
